LHC abort gap monitor electronics upgrade

### 2024-05-08 bibliography.tex

>>>>

        \bibitem{ibms} Guerrero, A., Jakob, H., Jones, R., Savioz, J.J,
        \emph{The SPS Individual Bunch Measurement System}. (2001), DIPAC 2001, Grenoble, \url{https://accelconf.web.cern.ch/d01/papers/PM12.pdf}

        \bibitem{fesa} Arruat, M., Fernanderz, L., Jackson, S., Locci, F., Nougaret, J.L., Peryt, M., Radeva, A., Sobczak, M., Vanden Eynden, M., (2007), ICALEPCS2007, \url{https://accelconf.web.cern.ch/ica07/TALKS/WOPA04_TALK.PDF}
